Draft

### 2017-03-04 Draft/sections/misc-math.tex
[minor] Notes about definition of functional derivative, and something trivial about using imaginary time.

Now as $z\to\infty$, we have
\begin{align}
    \int_0^\infty \dd{x} e^{\ln(x^z)-x}
    &\approx e^{-z+\ln(z^z)} \int_{-\infty}^\infty \dd{y} e^{- \frac{1}{2z}y^2} 
    = e^{z(\ln(z)-1)} \sqrt{2\pi z} \nonumber\\
    &= e^{\ln(z^z)}e^{-z}\sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{align}
Thus we have
\begin{equation}
    \Gamma(z+1) \overset{z\to\infty}{\approx} e^{z(\ln(z)-1)} \sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{equation}
For $z\in\C$, $\Re(z)>0$.
\subsection{Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
\label{sec:Funcation satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}

@@

But there is one pitfall that confuses me for a long time. Because:
\begin{align*}
    \int\dd{x}g(x)x\delta'(x) = -\int\dd{x}(g(x)+xg'(x))\delta(x)
    = -\int\dd{x}g(x)\delta(x)
\end{align*}
This lures me into believing
\begin{equation}
    x\delta'(x) = -\delta(x)
    \label{eq:xdp--d}
\end{equation}
Hence
\begin{equation}
    \delta'(x) = -\frac{\delta(x)}{x}
    \label{eq:dp--dx}
\end{equation}
While \ref{eq:xdp--d} is correct, \ref{eq:dp--dx} is of course wrong.
\subsection{Common Pitfalls}
\label{sec:Common Pitfalls}
    \subsubsection{Tensors}
    \label{sec:Tensors}

>>>>

Now as $z\to\infty$, we have
\begin{align}
    \int_0^\infty \dd{x} e^{\ln(x^z)-x}
    &\approx e^{-z+\ln(z^z)} \int_{-\infty}^\infty \dd{y} e^{- \frac{1}{2z}y^2} 
    = e^{z(\ln(z)-1)} \sqrt{2\pi z} \nonumber\\
    &= e^{\ln(z^z)}e^{-z}\sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{align}
Thus we have
\begin{equation}
    \Gamma(z+1) \overset{z\to\infty}{\approx} e^{z(\ln(z)-1)} \sqrt{2\pi z}
    = (\frac{z}{e})^z \sqrt{2\pi z}
\end{equation}
For $z\in\C$, $\Re(z)>0$.
\subsection{Function satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}
\label{sec:Function satisfying \texorpdfstring{$f(x+y)=f(x)f(x)$}{}}

@@

But there is one pitfall that confuses me for a long time. Because:
\begin{align*}
    \int\dd{x}g(x)x\delta'(x) = -\int\dd{x}(g(x)+xg'(x))\delta(x)
    = -\int\dd{x}g(x)\delta(x)
\end{align*}
This lures me into believing
\begin{equation}
    x\delta'(x) = -\delta(x)
    \label{eq:xdp--d}
\end{equation}
Hence
\begin{equation}
    \delta'(x) = -\frac{\delta(x)}{x}
    \label{eq:dp--dx}
\end{equation}
While \ref{eq:xdp--d} is correct, \ref{eq:dp--dx} is of course wrong.
\subsection{A beautiful product for sine function}

We have:
\begin{equation}
    \sin(x) =  x\prod_{n=1}^\infty \left(1-\frac{x^2}{n^2\pi^2}\right)
\end{equation}
Obviously the left and right has the same roots. But the proof of equality needs
some work. See related links:
\begin{enumerate}
    \item  
        \href{http://math.stackexchange.com/questions/674769/sinx-infinite-product-formula-how-did-euler-prove-it}{Phy.SE:
        $sin(x)$ infinite product formula: how did Euler prove it?},
    \item \href{https://en.wikipedia.org/wiki/Basel_problem}{Wikipedia-Basel Problem}.
\end{enumerate}

This formula is also used in calculating a path integral, see pp.114 of
\cite{Altland2010}.

\subsection{Functional Derivative}

The following is an answer to a question posted on Physics.StackExchange. It
contains a good definition of functional derivative and a specific example. The
link to that post is
\url{http://physics.stackexchange.com/questions/314638/variational-derivative-of-function-with-respect-to-its-derivative}.

The question asks:
\begin{myquote} \enquote{
    What is 
    $$ \frac{\delta f(t)}{\delta \dot{f}(t)} $$
    Where $\dot{f}(t)=df/dt$.
} \end{myquote}

The best answer is:
\begin{myquote} \enquote{
    The definition of the functional derivative of a functional $I[g]$ is the
    distribution $\frac{\delta I}{\delta g}(\tau)$ such that 
    $$\left\langle \frac{\delta I}{\delta g}, h\right\rangle 
        := \frac{d}{d\alpha}\bigg\rvert_{\alpha=0} I[g+ \alpha h]$$
    for every test function $h$. In our case, assuming to deal with functions which
    suitably vanish before reaching $\pm \infty$,
    $$I[g] = \int_{-\infty}^t g(x)dx$$
    so that
    $$I[\dot{f}]= f(t)$$
    as requested. Going on with the procedure
    $$\left\langle \frac{\delta I}{\delta g}, h\right\rangle 
        = \frac{d}{d\alpha}|_{\alpha=0}  \int_{-\infty}^t(g(\tau)+ \alpha h(\tau)) d\tau 
        = \int_{-\infty}^t h(\tau) dx 
        = \int_{-\infty}^{+\infty} \theta(t-\tau)h(\tau) d\tau
    $$
    where $\theta(\tau)=1$ for $\tau\geq 0$ and $\theta(\tau)=0$ for $\tau<0$
    and so 
$$\frac{\delta f(t)}{\delta \dot{f}}(\tau) = \frac{\delta I}{\delta g}(\tau)= \theta(t-\tau)$$
} \end{myquote}
In my opinion, the answer has assumed a inner product 
$$\left\langle f,g \right\rangle := \int f(t)g(t)\dd{t}$$.

\subsection{Common Pitfalls}
\label{sec:Common Pitfalls}
    \subsubsection{Tensors}
    \label{sec:Tensors}
